Evaluation of probabilistic photometric redshift estimation approaches for \textsc{LSST}

### 2019-03-14 paper/tex/methods.tex
finished delight

\delight \footnote{\url{https://github.com/ixkael/Delight}} \citep{Leistedt:17} is a hybrid technique that infers \pz s with a data-driven model of latent SEDs and a physical model of photometric fluxes as a function of redshift.
Generally, machine learning methods rely on representative training data with shared band passes, while template based methods rely on a complete library of templates based on physical models constructed.
\delight\ aims to take the best aspects of both approaches by constructing a large collection of latent SED templates (or physical flux-redshift models) from training data, with a template SED library as a guide to the learning of the model, thereby circumventing the machine learning prerequisite of representative training data in the same photometric bands and the template fitting requirement of detailed galaxy SED models.

Each test set galaxy $i$ has a posterior $p(z \vert \mathbf{\hat{F}}) \approx \sum_i p(\mathbf{\hat{F}} \vert z, T_i) p(z \vert T_i) p(T_i)$ of redshift $z$ conditioned on noisy flux $\mathbf{\hat{F}}$, where $p(z \vert T_i) p(T_i)$ captures prior information about the redshift distributions and abundances of the galaxy templates $T_i$.
As in traditional template fitting, each likelihood $p(\mathbf{\hat{F}} \vert \mathbf{F})$ relates the noisy flux $\mathbf{\hat{F}}$ with the noiseless flux $\mathbf{F}$ predicted by the model of a linear combination of templates, carefully constructed to account for model uncertainties and different normalization of the same SED.
\delight\ models SEDs as a linar combination of template SEDs plus Gaussian processes $F_b \sim \mathcal{GP}\left( \mu^F, k^F \right)$ with zero mean function $\mu^{F}$ and a physically motivated kernel $k^{F}$ that induces realistic correlations in flux-redshift space.

The machine learning approach appears in the inclusion of a pairwise comparison term $p(\mathbf{F} \vert z, z_j, \mathbf{\hat{F}}_j)$ for the prediction of flux at a redshift $z$ with respect to training set galaxy $j$ with redshift $z_j$ and flux $\mathbf{\hat{F}}_j$.
Thus the \pz\ posterior $p(\mathbf{\hat{F}} \vert z, T_i) = \int p(\mathbf{\hat{F}} \vert \mathbf{F}) p(\mathbf{F} \vert z, z_j, \mathbf{\hat{F}}_j) d\mathbf{F}$ may be interpreted as the probability that the training and the target galaxies have the same SED at a different redshift.
The flux prediction $p(\mathbf{F} \vert z, z_j, \mathbf{\hat{F}}_j)$ of the training galaxy at redshift $z$ is modeled via a Gaussian process,

The reader should refer to \citet{Leistedt:17} for further details.

In this study, all $100$ ordered Buzzard templates, as described in Section~\ref{sec:buzztemplates}, were used in \textsc{Delight}, and the Gaussian process was trained using the provided training sample.
Photometric uncertainties from the inputs are propagated into the code, while non-detections for each band are set to the mean of the respective bands.
The default settings of \textsc{Delight} were used, with the exception that the PDF bins were set to be linearly-spaced rather than logarithmic. In this study a flat prior in magnitude/type is assumed.

>>>>

\delight \footnote{\url{https://github.com/ixkael/Delight}} \citep{Leistedt:17} is a hybrid technique that infers \pz s with a data-driven model of latent SEDs and a physical model of photometric fluxes as a function of redshift.
Generally, machine learning methods rely on representative training data with shared photometric filters, while template based methods rely on a complete library of templates based on physical models constructed.
\delight\ aims to take the best aspects of both approaches by constructing a large collection of latent SED templates (or physical flux-redshift models) from training data, with a template SED library as a guide to the learning of the model, thereby circumventing the machine learning prerequisite of representative training data in the same photometric bands and the template fitting requirement of detailed galaxy SED models.
It models noisy observed flux $\mathbf{\hat{F}} = \mathbf{F} + F_{b}$ as a sum of a noiseless flux plus a Gaussian processes $F_b \sim \mathcal{GP}\left(\mu^F, k^F \right)$ with zero mean function $\mu^{F}$ and a physically motivated kernel $k^{F}$ that induces realistic correlations in flux-redshift space.

From a template-fitting perspective, each test set galaxy has a posterior $p(z \vert \mathbf{\hat{F}}) \approx \sum_i p(\mathbf{\hat{F}} \vert z, T_i) p(z \vert T_i) p(T_i)$ of redshift $z$ conditioned on noisy flux $\mathbf{\hat{F}}$, where $p(z \vert T_i) p(T_i)$ captures prior information about the redshift distributions and abundances of the galaxy templates $T_i$.
As in traditional template fitting, each likelihood $p(\mathbf{\hat{F}} \vert \mathbf{F})$ relates the noisy flux $\mathbf{\hat{F}}$ with the noiseless flux $\mathbf{F}$ predicted by the model of a linear combination of templates, carefully constructed to account for model uncertainties and different normalization of the same SED, plus the Gaussian process term.

The machine learning approach appears in the inclusion of a pairwise comparison term $p(\mathbf{F} \vert z, z_j, \mathbf{\hat{F}}_j)$ for the prediction of model flux $\mathbf{F}$ at a model redshift $z$ with respect to training set galaxy $j$ with redshift $z_j$ and observed flux $\mathbf{\hat{F}}_j$.
Thus the \pz\ posterior $p(\mathbf{\hat{F}} \vert z, T_i) = \int p(\mathbf{\hat{F}} \vert \mathbf{F}) p(\mathbf{F} \vert z, z_j, \mathbf{\hat{F}}_j) d\mathbf{F}$ may be interpreted as the probability that the training and the target galaxies have the same SED at different redshifts.
The flux prediction $p(\mathbf{F} \vert z, z_j, \mathbf{\hat{F}}_j)$ of the training galaxy at redshift $z$ is modeled via the Gaussian process described above; more detail is provided in \citet{Leistedt:17}.

In this study, the default settings of \delight\ were used, with the exception that the PDF bins were set to be linearly-spaced rather than logarithmic.
The Gaussian process was trained using the full DC1 training set.
We used the full DC1 template set with a flat prior in magnitude and SED type.
Photometric uncertainties from the inputs are propagated into the code, while non-detections for each band are set to the mean of the respective bands.
